Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-08 sas2015/content/concl.tex
add future work of adapting to IDE input problems

>>>>

As future work, it is possible to adapt our approach to work on IDE
problems in addition to IFDS problems. We would take an initial IDE
problem, convert it to a larger and more complex IDE problem, such
that the solution of the larger IDE problem generates a more precise
solution to the original IDE problem by removing infeasible paths due to
correlated calls.
